### 2020-06-21 ic-journal/multivariate.tex
Updated translations due to HOL updates (the only visible change is at BIGUNION)

Finally, the following two lemmas precisely estimate the free and
bound variables of a substituted term:
\begin{lemma}[\texttt{BV_SUBSET_BIGUNION}]
The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
are contained in the union of the bound variables in $E$ and \HOLinline{\HOLFreeVar{Ps}}.
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
\end{alltt}
\end{lemma}

\begin{lemma}[\texttt{FV_SUBSET_BIGUNION_PRO}]
The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
are contained in the union of the free variables in $E$ and \HOLinline{\HOLFreeVar{Ps}},
excluding \HOLinline{\HOLFreeVar{Xs}}.
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
\end{alltt}
\end{lemma}

>>>>

Finally, the following two lemmas precisely estimate the free and
bound variables of a substituted term:
\begin{lemma}[\texttt{BV_SUBSET_BIGUNION}]
The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
are contained in the union of the bound variables in $E$ and \HOLinline{\HOLFreeVar{Ps}}.
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
\end{alltt}
\end{lemma}

\begin{lemma}[\texttt{FV_SUBSET_BIGUNION_PRO}]
The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
are contained in the union of the free variables in $E$ and \HOLinline{\HOLFreeVar{Ps}},
excluding \HOLinline{\HOLFreeVar{Xs}}.
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
\end{alltt}
\end{lemma}

### 2020-06-21 paper/HOLMultivariate.tex
Updated code generations
Updated translations due to HOL updates (the only visible change is at BIGUNION)

\newcommand{\HOLMultivariateDate}{19 Novembre 2019}
\newcommand{\HOLMultivariateTime}{10:23}

@@

       \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}

@@

       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}

@@

       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}}
       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}

>>>>

\newcommand{\HOLMultivariateDate}{21 June 2020}
\newcommand{\HOLMultivariateTime}{18:11}

@@

       \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}

@@

       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}

@@

       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
